---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(okcupiddata)
```


# okcupiddata

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/okcupiddata)](http://cran.r-project.org/package=okcupiddata)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/okcupiddata)](http://www.r-pkg.org/pkg/okcupiddata)

R package of cleaned profile data **revised in 2021** from [OkCupid Profile Data for Introductory 
Statistics and Data Science 
Courses](https://doi.org/10.1080/10691898.2015.11889737) (Journal of 
Statistics Education 2015, revised in 2021): 59,946 OkCupid users who were living within 25 miles
of San Francisco, had active profiles during a period in the 2010s, were online in the 
previous year, and had at least one picture in their profile.

The data in this package are a "cleaned" version of the original data from the 
above paper, in that the following variables are modified for easier
use by novices:

* **Essay responses**: Due to file size restrictions, only the first 140 characters
of each user's first essay response (`essay0`: my self summary) are included. **revised in 2021**
* **Missing `income` values**: Previously coded as `-1`, they are now coded as `NA`
* **All other missing values**: Previously coded as `""`, they are now coded as `NA`
* **`offspring` and `sign`**: String instances of `"?&rsquo;"` are replaced with
apostrophes

**Note**:

* The original data, publication, code, and codebook can be found
[here](https://github.com/rudeboybert/JSE_OkCupid).
* The original data, and hence also this cleaned data, did not include
usernames.
* Permission to use this data was explicitly granted by OkCupid.



## Installation

Get the released version from CRAN:

```{r, eval = FALSE}
install.packages("okcupiddata")
```

Or the development version from GitHub:

```{r, eval = FALSE}
# If you haven't installed devtools yet, do so:
# install.packages("devtools")
devtools::install_github("rudeboybert/okcupiddata")
```



## Load Data

To load the profile data, run:

```{r, eval = FALSE}
data(profiles)
```

If you prefer having the 2021 revision of the published [Journal of Statistics 
Education](https://doi.org/10.1080/10691898.2015.11889737) data, which
also include the complete essay responses, then do not use this package; simply
run the following code:

```{r, eval=FALSE}
# Download the data (run only once):
url <- "https://github.com/rudeboybert/JSE_OkCupid/blob/master/profiles_revised.csv.zip?raw=true"
temp_zip_file <- tempfile()
download.file(url, temp_zip_file)
unzip(temp_zip_file, "profiles_revised.csv")
# Load CSV into R:
library(readr)
profiles_revised <- read_csv(file="profiles_revised.csv")
```

